---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# enRich

<!-- badges: start -->
<!-- badges: end -->

enrichR is a simple R package designed to interface with the Local Contexts Hub API.

## Installation

You can install the development version of enRich from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jacobgolan/enRich")
```

# Getting started

Install and load `enRich`

```{r example}
library(enRich)
```

`enRich` is a simple and easy to use package. Here is an index of its key functions:


```{r enRich}
?index.all.projects() # create a table of all projects in the LC Hub

?find.project.id() #search for a project's unique ID

?find.projects() #find and retrieve projects' metadata, notices and TK/BC labels

?readFASTA() #import a FASTA file into R

?outputFASTA() #export a FASTA file from R

?testFASTA() #create a dummy FASTA for learning
```

# **Step 1**: Importing Sequences
The function `testFASTA()` allows us to create a dummy FASTA for testing. You must specify the following arguments:

```{r pressure, echo = FALSE}
testFASTA(
  seqlength = c(75,100), # minimum and maximum sequence length range
  DNA_prob = rep(0.25,4), # relative freq of A, T, G, C
  no_seqs = 10, # how many sequences to simulate
  out.fasta = TRUE, #TRUE if you want to save a .fasta file to your computer
  file_name = "dsi", #only specify if out.fasta=TRUE
  loc = "LocusX" # locus name
)
```

When working with real data you will likely need to import a file from your computer into R. This can be done easily using `readFASTA()`

For simplicity, we will just read in the dummy FASTA we just created with `testFASTA()`. But in practice you can read in an FASTA file downloaded from NCBI, custom created, etc.

```{r}
dsi<-readFASTA("dsi.fasta")

```
Running either `testFASTA()` or `readFASTA()` results in a dataframe with two columns. The first column is the sequence name (header) and the second column is the sequence itself.


```{r, echo=T}
testFASTA(
  seqlength = c(75,100), # minimum and maximum sequence length range
  DNA_prob = rep(0.25,4), # relative freq of A, T, G, C
  no_seqs = 10, # how many sequences to simulate
  out.fasta = TRUE, #TRUE if you want to save a .fasta file to your computer
  file_name = "dsi", #only specify if out.fasta=TRUE
  loc = "LocusX" # locus name
)
```









